---
title: "Analysis of Beer Awards in the US"
author: "Adriana Picoral"
date: "November 10, 2020"
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Formatting

## Text Formatting

You can make words **bold** or *italics*.

You can also underscore for __bold__ or _italics_.

## Lists

There are two types of lists

- first bullet list item
- second bullet list item

1. first numbered list item
1. second numbered list item
1. third numbered list item

## Quotes

> This is a quote from someone

# Beer Award Analysis

## Data Description

The data comes from the [Great American Beer Festival](https://www.greatamericanbeerfestival.com/the-competition/winners/). 

```{r message=FALSE, echo=FALSE}
# load libraries
library(tidyverse)
library(knitr)
```

```{r}
# read data in
beer_awards <- read_csv("data/clean_beer_awards.csv")
#beer_awards <- read_csv("https://raw.githubusercontent.com/esoc214/fall2020_002_class_scripts/main/data/clean_beer_awards.csv")
```

## Data Questions

My data questions are as follows:

1. Which region in the US has the most beer awards?
1. Which type of beer gets the most awards across different regions in the US?

## Number of Awards per Region

```{r}
# start with beer_awards data and then
# filter District of Columbia out and then
# count region
beer_awards %>%
  filter(region != "District of Columbia") %>%
  count(region) %>%
  arrange(-n) %>%
  kable(col.names = c("Regions in the US", "Total Awards"),
        caption = "Total number of beer awards per region in the US.")
```

Regarding my first data question (i.e., *Which region in the US has the most beer awards?*), the West has the most awards.

## Beer Type per Region

```{r}
# start with beer_awards and then
# filter to keep regions that are different from "District of Colombia"
# count macro_category per region
beer_awards %>%
  filter(region != "District of Colombia") %>%
  count(macro_category, region)
```

