---
title: "Women Entrepreneurship by Country"
author: "Adriana Picoral"
date: "12/1/2020"
output: html_document
---

```{r setup, include=FALSE}
# load libraries
library(janitor)
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

# read data in
women_entrepreneur_data <- read_delim("data/women_in_labor_force.csv",
                                      delim = ";") %>%
  clean_names()
```

# Introduction

In this paper, I will discuss the effect of having women entrepreneurs on a country's economy. 

# Methods

## Research Questions

My research questions are as follows:

1. What is the relationship between having entrepreneurs in a country (no matter the gender) and that country's economy?
1. What is the relationship between having **women** entrepreneurs in a country and that country's economy?
1. Do women entrepreneurship index have a greater impact in the economy of a country than just entrepreneurs in general?

## Data

The data I am using was obtained from [Kaggle](https://www.kaggle.com/babyoda/women-entrepreneurship-and-labor-force) and contains the following variables: `r colnames(women_entrepreneur_data)`. The data was collected from the year 2015 from `r nrow(women_entrepreneur_data)` countries. 

# Analysis

The two variables we have available in the data regarding economic development are: 1) a binary variable called *level_of_development* (i.e., Developed vs. Developing) and 2) *inflation_rate*. The first step in the analysis is to establish whether inflation rate is lower or higher for developed countries, assuming that developed countries have better economies.

The box plot below shows that *developed* countries have a lower inflation rate than *developing* countries. Thus, we assume that the lower the inflation rate, the stronger a country's economy is. 

```{r}
# draw box plot of level_of_development vs. inflation_rate
women_entrepreneur_data %>%
  ggplot(aes(x = level_of_development,
             y = inflation_rate)) +
  geom_boxplot() +
  theme_linedraw() +
  labs(x = "Level of Development",
       y = "Inflation Rate",
       title = "Inflation by Development")
```

To answer my first research question (i.e., *What is the relationship between having entrepreneurs in a country (no matter the gender) and that country's economy?*), we need to establish the relationship between inflation and entrepreneurship index.

The scatter plot below shows that as entrepreneurship increases, inflation rate decreases, indicating that more people owning business is good for the economy of a country.

```{r}
# draw the scatter plot of inflation_rate vs. entrepreneurship index
women_entrepreneur_data %>%
  ggplot(aes(x = entrepreneurship_index,
             y = inflation_rate)) +
  geom_point() +
  geom_smooth(method = "lm",
              formula = y ~ x) +
  theme_linedraw() +
  labs(x = "Entrepreneurship Index",
       y = "Inflation Rate",
       title = "Inflation by Entrepreneurship")
```


# Conclusion